An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-23 neurips-19/poly-embed.tex
consistency

We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
\raft{Cut generic loss}%(A generic loss will be written $L:\R\to\reals^\Y$.)
We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
The \emph{Bayes risk} of a loss $L:\reals^d\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{u\in\reals^d} \inprod{p}{L(u)}$; naturally for discrete losses we write $\risk{\ell}$ (and the infimum is over $\R$).

@@

Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
\raft{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
For example, the \emph{mode} is the %finite
property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
% This terminology comes from the information elicitation \jessiet{information vs property... do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.

@@

To assess whether a surrogate and link function align with the original loss, we turn to the common condition of \emph{calibration}.
Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal.
\raft{Separated stuff commented out}
% , which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.

@@

\begin{definition}
  \label{def:calibrated}
  Let original loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
  We say $(L,\psi)$ is \emph{calibrated} with respect to $\ell$ if
for all $p \in \simplex$,
  \begin{equation}
    \label{eq:calibrated}
  \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.
  \end{equation}
\end{definition}
It is well-known that calibration implies \emph{consistency}, in the sense that
\raf{rough definition here}~\cite{agarwal2015consistent}.

@@

  %\raft{Jessie: I commented out your version below the proof.  What I have is on the informal side (so not necessarily better than what you had), mostly because of the ``working in the affine hull'' bit.  It can all be formalized though: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.  I can explain more on a call...}
  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
  In what follows, we implicitly work in the affine hull of $\simplex$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the (relative) interior of $\simplex$.
  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
  The projection of its epigraph $E_\ell$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.

>>>>

We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
\btw{Cut generic loss}%(A generic loss will be written $L:\R\to\reals^\Y$.)
We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
The \emph{Bayes risk} of a loss $L:\reals^d\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{u\in\reals^d} \inprod{p}{L(u)}$; naturally for discrete losses we write $\risk{\ell}$ (and the infimum is over $\R$).

@@

Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
\btw{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
For example, the \emph{mode} is the %finite
property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
% This terminology comes from the information elicitation \jessiet{information vs property... do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.

@@

To assess whether a surrogate and link function align with the original loss, we turn to the common condition of \emph{calibration}.
Roughly, a surrogate and link are calibrated if the best possible expected loss achieved by linking to an incorrect report is strictly suboptimal.
\btw{Separated stuff commented out}
% , which require that the excess loss of some report is bounded by (a constant times) the excess loss of the linked report.

@@

\begin{definition}
  \label{def:calibrated}
  Let original loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
  We say $(L,\psi)$ is \emph{calibrated} with respect to $\ell$ if
for all $p \in \simplex$,
  \begin{equation}
    \label{eq:calibrated}
  \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.
  \end{equation}
\end{definition}
It is well-known that calibration implies \emph{consistency}, in the following sense~\cite{agarwal2015consistent}.
Fix a fixed distribution $D \in \Delta(\X\times\Y)$, and let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
Then $(L,\psi)$ is consistent if a sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, then the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
As Definition~\ref{def:calibrated} does not involve the feature space $\X$, we will drop it for the remainder of the paper.

@@

    \btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.  It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
  In what follows, we implicitly work in the affine hull of $\simplex$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the (relative) interior of $\simplex$.
  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
  The projection of its epigraph $E_\ell$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.
